\sysfull

### 2018-08-04 paper/asplos19/coalescing.tex
change the env for the coalescing equations

An effective colescing strategy must be {\em aggressive} enough, attempting to coalesce a
large number of tasks to amortize a large amount of commit overhead. However, it must be 
{\em conservative} enough, attempting to coalesce only as many tasks as will execute
to completion given a certain energy conditions, reducing the risk or coalesced task re-execution penalty.

% An effective coalescing strategy moderates the risk of a power failure during a
% long coalesced task and capitalizes on the benefits of deferred commits by
% adapting the target size of the dynamic task to the energy available at
% runtime. 
%
\begin{figure}{t}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	%
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$z$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
% \end{wrapfigure}
\end{figure}
% 
\subsection{Task Coalescing Strategies} 
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i$th task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

possible coalescing strategies that we developed for \sys. 

@@

\subsubsection{Energy-oblivious Coalescing (EO)}

@@

A very simple {\em energy-oblivious} coalescing strategy treats all tasks as

@@

\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{commit}(B) = B + x$; 
\end{itemize}

@@

The History-Guided (HG) coalescing strategy adapts the coalescing target more

@@

The HG algorithm is characterized by the following functions: 
%
\begin{itemize}
\item $f_\text{reboot}(H) = \lfloor(H / 2)\rfloor;$
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{commit}(B) = \lfloor(B / 2)\rfloor;$ 
\end{itemize}
%
Fig.~\ref{fig:hg-coal} illustrates the operation of the history-guided
coalescing strategy.
The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$.
Based on that, $B$ is initially set to two and then decreases to one. Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the conservative approach. After the power failure, HG
uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$
and continue execution.
%
\subsubsection{Weighted History-Guided Coalescing (WHG)}
\label{subsec:energyTaskAware}
%
The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EO and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.

>>>>

An effective colescing strategy must be {\em aggressive} enough, attempting to coalesce a
large number of tasks to amortize a large amount of commit overhead. However, it must also be 
{\em conservative} enough, attempting to coalesce only as many tasks as will execute
to completion given a certain energy conditions, reducing the risk or long coalesced task re-execution penalty.

% An effective coalescing strategy moderates the risk of a power failure during a
% long coalesced task and capitalizes on the benefits of deferred commits by
% adapting the target size of the dynamic task to the energy available at
% runtime. 
%
\begin{figure}{t}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	%
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$z$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
% \end{wrapfigure}
\end{figure}
% 
\subsection{Task Coalescing Strategies} 
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i$th task
executed since the last power failure. $H$ (history) is the total number of
tasks between the last executed task and the power failure that preceding it.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight $W$ is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

possible coalescing strategies that we developed for \sys, albeit not the only possible. In fact, our system allows developers to design their own strategy to implement and link to Coala’s task scheduler. 

@@

\subsubsection{Energy-Oblivious Coalescing (EO)}

@@

A very simple {\em energy-Oblivious} coalescing strategy treats all tasks as

@@

\begin{equation}
	\begin{split}
		f_\text{reboot}(B)  		&	 = B - x \\
		f_\text{weight}(T_\text{i}) & 	 =  1 \\
		f_\text{commit}(B) 			& 	 = B + x
	\end{split}
\end{equation}

@@

The \emph{History-Guided} (HG) coalescing strategy adapts the coalescing target more

@@

The HG algorithm is characterized by the following functions: 
%
\begin{equation}
	\begin{split}
		 f_\text{reboot}(H) 			& = \lfloor(H / 2)\rfloor \\
		 f_\text{weight}(T_\text{i}) 	& =  1 \\
		 f_\text{commit}(B) 			& = \lfloor(B / 2)\rfloor
	\end{split}
\end{equation}
%
Fig.~\ref{fig:hg-coal} illustrates the operation of the history-guided
coalescing strategy.
The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$.
Based on that, $B$ is initially set to two and then decreases to one. Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the conservative approach. After the power failure, HG
uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$
and continue execution.
%
\subsubsection{Weighted History-Guided Coalescing (WHG)}
\label{subsec:energyTaskAware}
%
The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EO and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.
